Type Error Telemetry at Scale

### 2023-09-30 programming23/paper.tex
resize figures

\begin{figure}[t]\centering
  \includegraphics[width=.45\textwidth]{img/roblox-studio.png}
  \includegraphics[width=.45\textwidth]{img/roblox-studio-ide.png}
  \caption{{Roblox Studio 3D creation} tools (left) and IDE (right).}
  \label{fig:roblox-studio}
\end{figure}

@@

\begin{table}[t]\centering
  \caption{Session size in seconds and in number of records.}
  \label{t:session-size}
  %% NOTE max time = 1 million seconds = 15 days ...  +100 are over 2 days
  \begin{tabular}{lrrrrl} \\
    ~               & Mean & Stddev & Median & \ptile{99} & Distribution \\
    Time Span (sec) & 3,184 & \stddev{16} & 845 & 35,450 & \includegraphics[width=0.14\columnwidth,valign=M]{img/timespan-distribution.pdf} \\
    Record Count    & 286 & 583         & 138 & 3,302  & \includegraphics[width=0.14\columnwidth,valign=M]{img/event-count-distribution.pdf}
    %% TODO x-axis starts at 1
    %% TODO huge font, or smaller plot
  \end{tabular}
\end{table}

@@

\begin{table}[t]\centering
  \caption{Current type errors and \FS{} errors across all telemetry records.}
  \label{t:count-analysis-errors}
  \begin{tabular}[t]{ll} \\
    \begin{tabular}[t]{r@{~~}r@{~}r}
      595,137 & type errors \\
      289,698 & \hbox{}~in module & [\pct{48.68}] \\
       30,924 & \hbox{}~in edit range & [\pct{5.20}]
    \end{tabular}
    \begin{tabular}[t]{r@{~}r@{~}r}
      72,235,735 & {\FS{} errors} \\
      37,027,281 & \hbox{}~in module & [\pct{51.26}] \\
       1,111,178 & \hbox{}~in edit range & [\pct{1.54}]
    \end{tabular}
  \end{tabular}
\end{table}

@@

\begin{figure}[t]\centering
  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll}
      %% FILL bar chart? rectangle?
      \begin{tabular}[t]{r@{~~}l@{~}r}
         1,341,348 & \mnocheck{}          & [\pct{89.14}] \\
           156,883 & \mnonstrict{}        & [\pct{10.43}] \\
             6,505 & \mstrict{}           & [\pct{ 0.43}]
      \end{tabular}
      \begin{tabular}[t]{r@{~~}l@{~~}r}
      \end{tabular}
    \end{tabular}
    \caption{Analysis modes across the 1,504,736 records.}
    \label{f:total-records}
  \end{subfigure}

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll} \\
      \begin{tabular}[t]{r@{~~}r@{~}r}
        313,509 & \mnocheck{}   & [\pct{90.19}] \\
         32,902 & \mnonstrict{} & [\pct{ 9.47}] \\
            545 & \mstrict{}    & [\pct{ 0.16}] \\
            642 & mixed-mode    & [\pct{ 0.18}]
      \end{tabular}
      \begin{tabular}[t]{l@{~~}ll}
        %% TODO numbers may be off by +- 100
        %%    & 341 & contain a mode upgrade \\
        %%    & 320 & contain a mode downgrade \\
        %%    & 512 & contain modules with different modes
        %%  they don't match out/error-density*hasdown.rkt
        %%  ??? counting downs instead of sessions with downs ???
        %% TODO fix throughout paper!
        \zerowidth{Among the mixed-mode sessions:} \\
        & 176 & contain a mode upgrade \\
        & 233 & contain a mode downgrade \\
        & 512 & contain modules with different modes
      \end{tabular}
    \end{tabular}
    \caption{Analysis mode(s) for the 347,598 sessions.}
    \label{f:total-sessions}
  \end{subfigure}

@@

    \begin{tabular}[t]{cc}
    %% TODO why text blurry??!
    Type errors & Background errors \\
    \labelbars{\includegraphics[valign=M]{img/error-by-mode-te.pdf}}
    & \labelbars{\includegraphics[valign=M]{img/error-by-mode-fs.pdf}}
  \end{tabular}
  \caption{Type and \FS{} errors grouped by mode.}
  \label{f:error-by-mode}
\end{figure}

@@

  \mnocheck{}
  \includegraphics[width=\columnwidth]{img/error-count-nocheck-row--te-density-diff.pdf}
  \smallskip

  \mnonstrict{}
  \includegraphics[width=\columnwidth]{img/error-count-nonstrict-row--te-density-diff.pdf}
  \smallskip

@@

\begin{figure}[t]\centering
  %% TODO
  %% - thin bars
  %% - colors for good , bad (disagree) , neutral
  \begin{tabular}{lll}
    \mnocheck{} & \mnonstrict{} & \mstrict{} \\
    \includegraphics[width=0.26\columnwidth]{img/compass-nocheck.pdf}
    &
    \includegraphics[width=0.26\columnwidth]{img/compass-nonstrict.pdf}
    &
    \includegraphics[width=0.26\columnwidth]{img/compass-strict.pdf}
  \end{tabular}
  \caption{Comparing the change in type errors to the change in \FS{} errors.}
  \label{f:tefs-compass}
\end{figure}

>>>>

\begin{figure}[t]\centering
  \includegraphics[width=.35\textwidth]{img/roblox-studio.png}
  \hspace{1cm}
  \includegraphics[width=.35\textwidth]{img/roblox-studio-ide.png}
  \caption{{Roblox Studio 3D creation} tools (left) and IDE (right).}
  \label{fig:roblox-studio}
\end{figure}

@@

\begin{table}[t]\centering
  \caption{Session size in seconds and in number of records.}
  \label{t:session-size}
  %% NOTE max time = 1 million seconds = 15 days ...  +100 are over 2 days
  \begin{tabular}{lrrrrl}
    ~               & Mean & Stddev & Median & \ptile{99} & Distribution \\
    Time Span (sec) & 3,184 & \stddev{16} & 845 & 35,450 & \includegraphics[width=0.14\columnwidth,valign=M]{img/timespan-distribution.pdf} \\
    Record Count    & 286 & 583         & 138 & 3,302  & \includegraphics[width=0.14\columnwidth,valign=M]{img/event-count-distribution.pdf}
    %% TODO x-axis starts at 1
    %% TODO huge font, or smaller plot
  \end{tabular}
\end{table}

@@

\begin{table}[t]\centering
  \caption{Current type errors and \FS{} errors across all telemetry records.}
  \label{t:count-analysis-errors}
  \begin{tabular}[t]{ll}
    \begin{tabular}[t]{r@{~~}r@{~}r}
      595,137 & type errors \\
      289,698 & \hbox{}~in module & [\pct{48.68}] \\
       30,924 & \hbox{}~in edit range & [\pct{5.20}]
    \end{tabular}
    \begin{tabular}[t]{r@{~}r@{~}r}
      72,235,735 & {\FS{} errors} \\
      37,027,281 & \hbox{}~in module & [\pct{51.26}] \\
       1,111,178 & \hbox{}~in edit range & [\pct{1.54}]
    \end{tabular}
  \end{tabular}
\end{table}

@@

\begin{figure}[t]\centering
  \begin{subfigure}[b]{0.48\columnwidth}
      \begin{tabular}[t]{r@{~~}l@{~}r}
         1,341,348 & \mnocheck{}          & [\pct{89.14}] \\
           156,883 & \mnonstrict{}        & [\pct{10.43}] \\
             6,505 & \mstrict{}           & [\pct{ 0.43}]
      \end{tabular}
    \caption{Analysis modes in 1,504,736 records.}
    \label{f:total-records}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\columnwidth}
      \begin{tabular}[t]{r@{~~}r@{~}r}
        313,509 & \mnocheck{}   & [\pct{90.19}] \\
         32,902 & \mnonstrict{} & [\pct{ 9.47}] \\
            545 & \mstrict{}    & [\pct{ 0.16}] \\
            642 & mixed-mode    & [\pct{ 0.18}]
      \end{tabular}
    \caption{Analysis mode(s) in 347,598 sessions.}
    \label{f:total-sessions}
  \end{subfigure}

  {Among the mixed-mode sessions:
        176 contain a mode upgrade,
        233 contain a mode downgrade, and
        512 contain modules with different modes.}

@@

    \begin{tabular}[t]{cc}
    %% TODO why text blurry??!
    Type errors & Background errors \\
    \labelbars{\includegraphics[width=0.20\columnwidth,valign=M]{img/error-by-mode-te.pdf}}
    & \labelbars{\includegraphics[width=0.20\columnwidth,valign=M]{img/error-by-mode-fs.pdf}}
  \end{tabular}
  \caption{Type and \FS{} errors grouped by mode.}
  \label{f:error-by-mode}
\end{figure}

@@

  \mnocheck{}
  \includegraphics[width=\columnwidth]{img/error-count-nocheck-row--te-density-diff.pdf}

  \mnonstrict{}
  \includegraphics[width=\columnwidth]{img/error-count-nonstrict-row--te-density-diff.pdf}

@@

\begin{figure}[t]\centering
  %% TODO
  %% - thin bars
  %% - colors for good , bad (disagree) , neutral
  \begin{tabular}{lll}
    \mnocheck{} & \mnonstrict{} & \mstrict{} \\
    \includegraphics[width=0.24\columnwidth]{img/compass-nocheck.pdf}
    &
    \includegraphics[width=0.24\columnwidth]{img/compass-nonstrict.pdf}
    &
    \includegraphics[width=0.24\columnwidth]{img/compass-strict.pdf}
  \end{tabular}
  \caption{Comparing the change in type errors to the change in \FS{} errors.}
  \label{f:tefs-compass}
\end{figure}
